Calibration tests beyond classification

### 2021-03-18 paper/main.tex
Correct equation (2) and add explanation

% abbreviations
\DeclareMathOperator{\Prob}{\mathbb{P}}
\DeclareMathOperator{\Exp}{\mathbb{E}}
\DeclareMathOperator{\Var}{\mathbb{V}}
\DeclareMathOperator{\Cov}{\mathbb{C}}
\DeclareMathOperator*{\esssup}{ess\,sup}
\DeclareMathOperator{\argmax}{arg\,max}

@@

If $P$ is a classification model, \cref{def:calibration} coincides
with the notion of (multi-class) calibration by
\citet{Broecker2009,Vaicenavicius2019,Kull2019}. Alternatively, in classification
some authors~\citep{Naeini2015,Guo2017,Kumar2018} study the
strictly weaker property of confidence calibration~\citep{Kull2019},
which only requires
\begin{equation}\label{eq:calibration_confidence}
    \Prob{(Y = y | \argmax {P_X} = y)} = \max P_X \qquad \text{almost surely}
\end{equation}
to hold for every target $y$.

>>>>

% abbreviations
\DeclareMathOperator{\Prob}{\mathbb{P}}
\DeclareMathOperator{\Exp}{\mathbb{E}}
\DeclareMathOperator{\Var}{\mathbb{V}}
\DeclareMathOperator{\Cov}{\mathbb{C}}
\DeclareMathOperator{\Ber}{Ber}
\DeclareMathOperator*{\esssup}{ess\,sup}
\DeclareMathOperator{\argmax}{arg\,max}

@@

If $P$ is a classification model, \cref{def:calibration} coincides
with the notion of (multi-class) calibration by
\citet{Broecker2009,Vaicenavicius2019,Kull2019}. Alternatively, in classification
some authors~\citep{Naeini2015,Guo2017,Kumar2018} study the
strictly weaker property of confidence calibration~\citep{Kull2019},
which only requires
\begin{equation}\label{eq:calibration_confidence}
    \Prob{(Y = \argmax{P_X} | \max P_X)} = \max P_X \qquad \text{almost surely}.
\end{equation}
This notion of calibration corresponds to calibration according to \cref{def:calibration}
for a reduced problem with binary targets
$\widetilde{Y} \coloneqq \mathbbm{1}(Y = \argmax{P_X})$ and Bernoulli
distributions $\widetilde{P}_X \coloneqq \Ber(\max P_X)$ as probabilistic models.
